Global SOC maps and emissions

### 2020-12-10 ResultNotebooks/results_SOCcompare.Rmd
mayor update on figures and flowfig

```{r load}
library(mrcommons)
library(mrvalidation)
library(mrSOCbudget)
library(magpiesets)

rev       <- "rev0.76baseline"
outputdir <- "Output/Images/"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
#untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data", extras="--keep-newer-files ")

SoilCarbon <- read.magpie("Data/Baseline/SoilCarbon.rds")
Landuse    <- read.magpie("Data/Baseline/Landuse.rds")

@@

SOCStock     <- dimSums(dimSums(SoilCarbon[,,"actualstate"], dim=3.3)* Landuse, dim=3)
glo_SOCStock <- dimSums(SOCStock, dim=1) 
cell2iso     <- toolGetMapping("CountryToCellMapping.csv", type = "cell")
iso_SOCStock <- toolCountryFill(toolAggregate(SOCStock, rel=cell2iso, from="celliso", to="iso", dim=1), fill=0)
iso2reg      <- toolMappingFile("regional",getConfig("regionmapping"),readcsv = TRUE)
reg_SOCStock <- toolAggregate(iso_SOCStock, rel=iso2reg, from="CountryCode", to="RegionCode")

print(dimSums(dimSums(SoilCarbon[,,"actualstate"], dim=3.3)* Landuse, dim=c(1,3)))

@@

  LPJ_IPCC   <- calcOutput("ValidCarbonStocks", datasource = "LPJ_IPCC2006", aggregate="REG+GLO", try=TRUE)
  #LPJ_rev21  <- calcOutput("ValidCarbonStocks", datasource = "LPJmL_rev21", aggregate="REG+GLO", try=TRUE)
  #LPJ_car    <- calcOutput("ValidCarbonStocks", datasource = "LPJmLCarbon", aggregate="REG+GLO", try=TRUE)
  WISE       <- calcOutput("ValidCarbonStocks", datasource = "WISE", aggregate="REG+GLO", try=TRUE)
  GSOC       <- calcOutput("ValidCarbonStocks", datasource = "GSOC", aggregate="REG+GLO", try=TRUE)
  SoilGrids  <- calcOutput("ValidCarbonStocks", datasource = "SoilGrids", aggregate="REG+GLO", try=TRUE)
  LPJmL4  <- calcOutput("ValidCarbonStocks", datasource = "LPJmL4Paper", aggregate="REG+GLO", try=TRUE)

@@

Plot global stocks

```{r plot glo stocks}

plot(c(getYears(glo_SOCStock, as.integer=TRUE)), glo_SOCStock, type="l", col="red", xlim=c(1951,2017),  ylim=c(350000,1300000))
lines(getYears(LPJ_IPCC, as.integer = TRUE), LPJ_IPCC["GLO",,1], type="l", col="green")
#lines(getYears(LPJ_car, as.integer = TRUE), LPJ_car["GLO",,], type="l", col="darkgreen")
lines(getYears(LPJmL4, as.integer = TRUE), LPJmL4["GLO",,], type="l", col="lightgreen")
lines(getYears(WISE, as.integer = TRUE), WISE["GLO",,], type="l", col="brown")
lines(getYears(SoilGrids, as.integer = TRUE), SoilGrids["GLO",,], type="l", col="blue")
lines(getYears(GSOC, as.integer = TRUE), GSOC["GLO",,], type="l", col="pink")
plot(c(getYears(glo_SOCStock, as.integer=TRUE)), glo_SOCStock, type="l", col="red")
```

```{r table ipcc scf}

@@

@@

glob
ggsave(paste0(outputdir,"/glo_comparisonfigure.png"), plot=glob)
```

```{r plot diff maps, out.width="100%", out.height=1000}

library(luplot)
library(magpiesets)

cellSOCdens   <- (dimSums(dimSums(SoilCarbon[,,"naturalstate"], dim=3.2) * Landuse, dim=c(3))/dimSums(Landuse, dim=c(3)))[,findset("past"),]
cellSOCdens[is.na(cellSOCdens)] <- 0

cellSoilGrids <- readSource("SoilGrids", subtype="cstock_0_30", convert="onlycorrect")
cellLPJml     <- calcOutput("LPJmL", version="LPJmL4", climatetype="CRU_4", subtype="soilc_layer", time="raw", selectyears="past", aggregate=FALSE)
cellLPJml     <- collapseNames(cellLPJml[,,"layer1"]+1/3*cellLPJml[,,"layer2"], collapsedim = c(2,3))

diffSoilGrids <- cellSOCdens - cellSoilGrids
diffLPJml     <- cellSOCdens - cellLPJml

luplot::plotmap(diffLPJml[,10,], legend_range = c(-80,80))
```

>>>>

```{r load}
library(mrcommons)
library(mrsoil)
library(magpiesets)

rev       <- "rev0.11"
outputdir <- "Output/"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
#untar(paste0(getConfig("outputfolder"),"/",rev,"histManagement_h12_carbonbudget.tgz"), exdir="Data/histManagement", extras="--keep-newer-files ")

SoilCarbon <- read.magpie("Data/histManagement/SoilCarbon.rds")
Landuse    <- read.magpie("Data/histManagement/Landuse.rds")

@@

SOCStock     <- dimSums(dimSums(SoilCarbon[,,"actualstate"], dim=3.3)* Landuse, dim=3)
glo_SOCStock <- dimSums(SOCStock, dim=1) 
cell2iso     <- toolGetMapping("CountryToCellMapping.csv", type = "cell")
iso_SOCStock <- toolCountryFill(toolAggregate(SOCStock, rel=cell2iso, from="celliso", to="iso", dim=1), fill=0)
iso2reg      <- read.csv2("Data/histManagement/regionmappingH12.csv")
reg_SOCStock <- toolAggregate(iso_SOCStock, rel=iso2reg, from="CountryCode", to="RegionCode")
```

@@

library(mrvalidation)

  LPJ_IPCC   <- calcOutput("ValidCarbonStocks", datasource = "LPJ_IPCC2006", aggregate="REG+GLO", try=TRUE)
  WISE       <- calcOutput("ValidCarbonStocks", datasource = "WISE", aggregate="REG+GLO", try=TRUE)
  GSOC       <- calcOutput("ValidCarbonStocks", datasource = "GSOC", aggregate="REG+GLO", try=TRUE)
  SoilGrids  <- calcOutput("ValidCarbonStocks", datasource = "SoilGrids", aggregate="REG+GLO", try=TRUE)
  LPJmL4     <- calcOutput("ValidCarbonStocks", datasource = "LPJmL4Paper", aggregate="REG+GLO", try=TRUE)

@@

```{r table glo soc stocks}

@@

supp.labs <- getNames(glo_SOC["GLO",,invert=TRUE])
names(supp.labs) <- c("OJ", "VC")

@@

glob
ggsave(paste0(outputdir,"/glo_comparisonfigure.png"), plot=glob)
```
`

### 2020-12-10 ResultNotebooks/results_SOCflows.Rmd
Mayor update of everything
mayor update on figures and flowfig

```{r load}
library(mrcommons)
library(mrvalidation)
library(mrSOCbudget)
library(magpiesets)

rev       <- "rev0.7_mrSOC"
outputdir <- "Output/Images"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
#untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data", extras="--keep-newer-files ")

@@

CarbonInput      <- readRDS("Data/CarbonInput.rds")
CarbonLitter     <- readRDS("Data/CarbonLitter.rds")
CarbonManure     <- readRDS("Data/CarbonManure.rds")           
CarbonResidues   <- readRDS("Data/CarbonResidues.rds")
CarbonHarvest    <- readRDS("Data/Crop_Harvest.rds")
SoilCarbonOut    <- readRDS("Data/SoilCarbon.rds")
SoilCarbonDecay  <- readRDS("Data/SoilDecay.rds")
SoilCarbonStSt   <- readRDS("Data/SoilSteadyState.rds")

Landuse          <- readRDS("Data/Landuse.rds")
LanduseChange    <- readRDS("Data/LanduseChange.rds")

FAOmassbalance   <- readRDS("Data/FAOmassbalance_ISO.rds" )
ManureExcreted   <- readRDS("Data/Manure_excreted.rds")
ManureRecycled   <- readRDS("Data/Manure_recycled.rds")
ResidueBiomass   <- readRDS("Data/Residue_Biomass.rds")
ResiduesAgDemand <- readRDS("Data/ResiduesAg_FieldBalance.rds")

@@

ActiveDecay        <- mbind(setNames(calcOutput("ActiveDecay",  landtype="crop",   aggregate = FALSE),"crop"),
                              setNames(calcOutput("ActiveDecay",  landtype="natveg", aggregate = FALSE),"natveg"))
SlowDecay          <- mbind(setNames(calcOutput("SlowDecay",  landtype="crop",   aggregate = FALSE),"crop"),
                              setNames(calcOutput("SlowDecay",  landtype="natveg", aggregate = FALSE),"natveg"))
PassiveDecay       <- mbind(setNames(calcOutput("PassiveDecay", landtype="crop",   aggregate = FALSE),"crop"),
                              setNames(calcOutput("PassiveDecay", landtype="natveg", aggregate = FALSE),"natveg"))

subpools     <- c("active","slow","passive")
names        <- as.vector(outer(getNames(Landuse), subpools, paste, sep="."))
Decay <- new.magpie(getCells(Landuse), getYears(Landuse), names, fill = 0)

@@

Biomass excreted ist bigger than feed intake via plant harvest and residues taken for feed.

```{r soc}

  Litter             <- dimSums(calcOutput("CarbonLitter", aggregate=FALSE)[,,"c"]*Landuse[,,"natveg"], dim=1)

  # Calculate effective input
  param <- readSource("IPCCSoil", convert=FALSE)
  param.f1_metab2a          <- setYears(param[,,"f1"], NULL) 
  # stabilization efficiencies for metabolic decay products entering the active pool
  param.f3_struc2s          <- setYears(param[,,"f3"], NULL) 
  # stabilization efficiencies for structural decay products entering the slow pool
  param.f2_struc2a <- mbind(setNames(setYears(param[,,"f2_ft"], NULL), "crop"),
                            setNames(setYears(param[,,"f2_nt"], NULL), "natveg"))
  # stabilization efficiencies for structural decay products entering the active pool (tillage and no tillage specific)

  cell.input       <- mbind(add_dimension(dimSums(calcOutput("CarbonInput", landtype="crop", aggregate = FALSE),dim=3.2),
                                          dim=3.1, nm = "crop",   add="landuse"),
                            add_dimension(collapseNames(calcOutput("CarbonInput", landtype="natveg", aggregate = FALSE)),
                                          dim=3.1, nm = "natveg", add="landuse"))
  CarbonInput      <- dimSums(cell.input[,,"totalC"]*Landuse, dim=c(1))

  CarbonInputEff   <- collapseNames(dimSums((cell.input[,,"metabDOC"] * param.f1_metab2a +
                                             cell.input[,,"strucDOC"] * param.f2_struc2a +
                                             cell.input[,,"ligninC"]  * param.f3_struc2s) * Landuse, dim=c(1)))

  CarbonInputTot   <- collapseNames(dimSums(SOC[,,"steadystate"]*SOC[,,"decayrate"]*Landuse, dim=c(1,3.3)))

  # Load inputs, active steady state stock and decay rate

  SOC                <- calcOutput("SoilCarbon", output="full", aggregate=FALSE)
  Landuse            <- calcOutput("Landuse",       aggregate=FALSE)
  LanduseChange      <- calcOutput("LanduseChange", aggregate=FALSE)

  CarbonStocks       <- collapseNames(dimSums(SOC[,,c("steadystate","actualstate")]*Landuse, dim=1))
  CarbonTransfer     <- dimSums(toolConditionalReplace(SOC[,,"carbontransfer"], "<0", 0),dim=c(1,3.3))
  CarbonRelease      <- collapseNames(dimSums(SOC[,,"interstate"]*SOC[,,"decayrate"]*Landuse, dim=c(1, 3.3)))

print(mbind(CarbonTransfer, CarbonRelease))
```

>>>>

```{r load}
library(mrcommons)
library(mrvalidation)
library(mrsoil)
library(magpiesets)

rev <- "rev0.78baseline"

outputdir <- "Output/Images"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data/Baseline", extras="--keep-newer-files ")

revfolder <- "Data/Baseline/"

@@

CarbonInput      <- readRDS(paste0(revfolder,"CarbonInput.rds"))
CarbonLitter     <- readRDS(paste0(revfolder,"CarbonLitter.rds"))
CarbonManure     <- readRDS(paste0(revfolder,"CarbonManure.rds"))          
CarbonResidues   <- readRDS(paste0(revfolder,"CarbonResidues.rds"))
CarbonHarvest    <- readRDS(paste0(revfolder,"Crop_Harvest.rds"))
SoilCarbonOut    <- readRDS(paste0(revfolder,"SoilCarbon.rds"))

Landuse          <- readRDS(paste0(revfolder,"Landuse.rds"))
LanduseChange    <- readRDS(paste0(revfolder,"LanduseChange.rds"))

FAOmassbalance   <- readRDS(paste0(revfolder,"FAOmassbalance_ISO.rds"))
ManureExcreted   <- readRDS(paste0(revfolder,"Manure_excreted.rds"))
ManureRecycled   <- readRDS(paste0(revfolder,"Manure_recycled.rds"))
ResidueBiomass   <- readRDS(paste0(revfolder,"Residue_Biomass.rds"))
ResiduesAgDemand <- readRDS(paste0(revfolder,"ResiduesAg_FieldBalance.rds"))

@@

ActiveDecay        <- mbind(setNames(calcOutput("ActiveDecay",  landtype="crop",   aggregate = FALSE),"crop"),
                              setNames(calcOutput("ActiveDecay",  landtype="natveg", aggregate = FALSE),"natveg"))
SlowDecay          <- mbind(setNames(calcOutput("SlowDecay",  landtype="crop",   aggregate = FALSE),"crop"),
                              setNames(calcOutput("SlowDecay",  landtype="natveg", aggregate = FALSE),"natveg"))
PassiveDecay       <- mbind(setNames(calcOutput("PassiveDecay", landtype="crop",   aggregate = FALSE),"crop"),
                              setNames(calcOutput("PassiveDecay", landtype="natveg", aggregate = FALSE),"natveg"))
decay <- calcOutput("Decay", aggregate = FALSE)
subpools     <- c("active","slow","passive")
names        <- as.vector(outer(getNames(Landuse), subpools, paste, sep="."))
Decay <- new.magpie(getCells(Landuse), getYears(Landuse), names, fill = 0)

@@

### 2020-12-10 ResultNotebooks/results_SOCmaps.Rmd
mayor update on figures and flowfig

```{r load}
library(mrcommons)
library(mrvalidation)
library(mrSOCbudget)
library(magpiesets)

rev       <- "rev0.76baseline"
outputdir <- "Output/Images"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
#untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data", extras="--keep-newer-files ")

SoilCarbon <- read.magpie("Data/Baseline/SoilCarbon.rds")
Landuse    <- read.magpie("Data/Baseline/Landuse.rds")

@@

SoilCarbon[,,"naturalstate.crop"] <- SoilCarbon[,,"naturalstate.natveg"]
SOCStock        <- dimSums(dimSums(SoilCarbon[,,"state",pmatch=TRUE], dim=3.3)* Landuse, dim=3.2)
glo_SOCStock    <- dimSums(SOCStock, dim=1) 
glo_SOCEmission <- (glo_SOCStock[,,"naturalstate"] - glo_SOCStock[,,"actualstate"])/1000
plot(getYears(glo_SOCEmission, as.integer = TRUE),glo_SOCEmission/1000, type="l", xlab="Time", ylab="Global SOC Debt in GtC")
plot(getYears(glo_SOCEmission, as.integer = TRUE),glo_SOCStock[,,"actualstate"])
lines(getYears(glo_SOCEmission, as.integer = TRUE),glo_SOCStock[,,"naturalstate"])

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission[,seq(1975,2010,5),])[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = "Global SOC gap\n in GtC") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(trans = squish_trans(-35,0,15),
                     limits = c(-45,0),
                     breaks = c(0, -15, -35, -40, -45)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 10, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size)#,
        #plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
        ) +
  annotate(geom="text", label="SOC debt", x=factor(1995), y=-35, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -39, arrow=arrow(end="both", type="closed", length=unit(0.1, "inches")))

@@

SOCincrease <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(increase2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(-100,100), colours = cols, 
                      name = expression("cropland SOC gap in tons of carbon per hectar"), 
                      values=(c(-100,-50,-20,-10,10,20,50,100)+100)/200,
                      breaks=c(-50,-20,-10,10,20,50,100),
                      labels=c("> -100    -50", "  -20","  -10","  10","  20","  50"," > 100"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

@@

SOCdensity <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(density2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(0,150), colours = cols, 
                      name = expression("cropland SOC in tons of carbon per hectar"), 
                      values=c(0,5,10,20,40,70,100,150)/150,
                      breaks=c(5,10,20,40,70,100,150),
                      labels=c("0     5","  10","  20","  40","  70","  100"," >150"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

@@

grid <- plot_grid(SOCdensity, SOCemis, SOCincrease, SOCshare, ncol=2, labels=c("a","b", "c", "d"),
                  label_fontface = "plain", label_size = 10)
grid
ggsave(paste0(outputdir,"/4panelfigure.png"), plot=grid, width = 20, height = 14, dpi = 300, units = "cm")

>>>>

```{r load}
library(mrcommons)
library(mrvalidation)
library(mrsoil)
library(magpiesets)

rev <- "rev0.11"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")

filesNeeded <- c("SoilCarbon.rds","Landuse.rds")

scenarios    <- c("histManagement","constManagement-1975", "constTillage-mixedtill", "constResidues-1975", "constManure-1975",
                  "constManagement2-1975", "constResrate-1975", "constYield-1975",
                 "Initial-natveg", "Initial-natveg_constManangement-1975", "Initial-natveg_constManangement2-1975", 
                 "LitterPNV-PerennialGrasses", "LitterPNV-AASS", "LitterPNV-BRCF", 
                 "LitterPNV-MTCF", "LitterPNV-BLEAF",  "LitterPNV-TREF")

# for(item in scenarios){
#    dir.create(path=paste0("Data/",paste0(rev,item)))
#    untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
#    files=filesNeeded, exdir=paste0("Data/", paste0(rev,item)), extras="--keep-newer-files ")
# }

outputdir <- "Output/Images"

SoilCarbon <- read.magpie(paste0("Data/histManagement/SoilCarbon.rds"))
Landuse    <- read.magpie(paste0("Data/histManagement/Landuse.rds"))

@@

SoilCarbon[,,"naturalstate.crop"] <- SoilCarbon[,,"naturalstate.natveg"]
SOCStock        <- dimSums(dimSums(SoilCarbon[,,"state",pmatch=TRUE], dim=3.3)* Landuse, dim=3.2)
glo_SOCStock    <- dimSums(SOCStock, dim=1) 
glo_SOCEmission <- (glo_SOCStock[,,"naturalstate"] - glo_SOCStock[,,"actualstate"])/1000

SoilCarbon <- SoilCarbon[,findset("past"),]
Landuse    <- Landuse[,findset("past"),]

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission[,seq(1975,2010,5),])[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = "Global SOC loss\n in GtC") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(trans = squish_trans(-18,0,10),
                     limits = c(-28,0),
                     breaks = c(0, -20, -22, -24, -26, -28)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 10, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size)#,
        #plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
        ) +
  annotate(geom="text", label="SOC debt", size=14, x=factor(1995), y=-20, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -24, arrow=arrow(end="both", type="closed", length=unit(0.1, "inches")))

@@

SOCincrease <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(increase2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(-100,100), colours = cols, 
                      name = expression("cropland SOC gap in tons of carbon per hectare"), 
                      values=(c(-100,-50,-20,-10,10,20,50,100)+100)/200,
                      breaks=c(-50,-20,-10,10,20,50,100),
                      labels=c("< -100    -50", "  -20","  -10","  10","  20","  50"," > 100"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

@@

SOCdensity <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(density2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(0,150), colours = cols, 
                      name = expression("cropland SOC in tons of carbon per hectare"), 
                      values=c(0,5,10,20,40,70,100,150)/150,
                      breaks=c(5,10,20,40,70,100,150),
                      labels=c("0     5","  10","  20","  40","  70","  100"," >150"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

@@

grid <- plot_grid(SOCdensity, SOCemis, SOCincrease, SOCshare, ncol=2, labels=c("(a)","(b)", "(c)", "(d)"),
                  label_fontface = "plain", label_size = 10)
grid
ggsave(paste0(outputdir,"/4panelfigure.png"), plot=grid, width = 20, height = 14, dpi = 300, units = "cm")
